Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/eval.tex
typo
eval nits

The \cc{zip\_file} grammarfirst splits the entire file stream into two
streams based on the \cc{zip\_end\_of\_directory} transform in line 2
%(whose two C function signatures are shown in Figure~\ref{fig:zip-eod-xform}). 
\cc{zip\_end\_of\_directory_parse}
finds the end-of-directory header as described above, by scanning the
file backwards, and splits the file into two streams, one containing
the end-of-directory header and one containing the file contents. The
\cc{end\_of\_directory} rule is then applied to the header stream in
line 4. All offsets in the ZIP file refer to the beginning of the
file, so the stream \cc{\$file} which contains the file contents
without the header is passed as an argument to all parsers from
hereon.

@@

The \cc{file} rule starting at line 41, describing a ZIP file entry takes dependent field
parameters containing file metadata information from the directory
header. However, this same information is duplicated in the file
entry, so the grammar uses the Nail-supplied \cc{u16\_depend}
transform to check whether the two values are equal. Unlike most other
transforms, \cc{u16\_depend} does not consume or produce strings; it
only checks that two dependent fields are equal when parsing, and
assigns the value of the second field to the first when generating.
This ensures that the programmer does not have to worry about
inconsistencies when handling the internal representation of a ZIP
file.

@@

\cc{unzip}
  & 220
  & 1,600
  & (Info-Zip) \\
\bottomrule
\end{tabular}
\caption{Comparison of code size for three applications written in Nail,and several existing alternative implementations.}
\label{fig:effort}
\end{figure}

@@

In \S\ref{s:motivation}, we found 14 input handling vulnerabilities related to ZIP files.

Ten of these vulnerabilities involved memory corruption during input handling.
Because Nail's generated code checks offsets before reading and does not
expose any untrusted pointers to the application, it is immune against
memory corruption attacks by design.

>>>>

The \cc{zip\_file} grammar first splits the entire file stream into two
streams based on the \cc{zip\_end\_of\_directory} transform on line 2.
%(whose two C function signatures are shown in Figure~\ref{fig:zip-eod-xform}). 
\cc{zip\_end\_of\_directory_parse}
finds the end-of-directory header as described above, by scanning the
file backwards, and splits the file into two streams, one containing
the end-of-directory header and one containing the file contents. The
\cc{end\_of\_directory} rule is then applied to the header stream in
line 4. All offsets in the ZIP file refer to the beginning of the
file, so the stream \cc{\$file} which contains the file contents
without the header is passed as an argument to all parsers from
hereon.

@@

The \cc{file} rule starting at line 41, describing a ZIP file entry,
takes dependent field
parameters containing file metadata information from the directory
header. However, this same information is duplicated in the file
entry, so the grammar uses the Nail-supplied \cc{u16\_depend}
transform to check whether the two values are equal. Unlike most other
transforms, \cc{u16\_depend} does not consume or produce strings; it
only checks that two dependent fields are equal when parsing, and
assigns the value of the second field to the first when generating.
This ensures that the programmer does not have to worry about
inconsistencies when handling the internal representation of a ZIP
file.

@@

\cc{unzip}
  & 220
  & 1,600
  & (Info-Zip) \\
\bottomrule
\end{tabular}
\caption{Comparison of code size for three applications written in
  Nail,and a comparable existing implementation without Nail.}
\label{fig:effort}
\end{figure}

@@

In \S\ref{s:motivation}, we found 15 input handling vulnerabilities
related to ZIP files.

11 of these vulnerabilities involved memory corruption during input handling.
Because Nail's generated code checks offsets before reading and does not
expose any untrusted pointers to the application, it is immune against
memory corruption attacks by design.
